\myTitle

### 2024-07-18 tex/supplemental-figures.tex
Boing
Getting WRAP stuff added in to repo and paper/supp

>>>>

%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\textwidth]{images/winter-v-non-winter-mh-plot_nind_ge10.pdf}
\caption[
	Absolute difference in allele frequency between winter run and non-winter run fish
]{
	\footnotesize Absolute difference in allele frequency between winter run and non-winter run fish of the CCV.
	The plot shows only those SNPs with at least a frequency difference of 0.5 between the two groups. Each point
	is a SNP. The  $x$ axis shows position in the Otsh\_v1.0 genome
	with color alternating by chromosome as indicated by RefSeq names on plot.
}
\label{fig:wrap-absdiff}
\end{figure}

%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\textwidth]{images/wrap-slide-window.pdf}
\caption[
	Sliding windows of absolute allele frequency difference between winter run and others
]{
	\footnotesize Values within 100 kb sliding windows of the fraction of sites with $|d|$ (absolute difference in
	allele frequency between winter run and non-winter run fish of the CCV) greater than 0.5 that also have
	$|d|>0.9$. The  $x$ axis shows position in the Otsh\_v1.0 genome
	with color alternating by chromosome as indicated by RefSeq names on plot. Red circles denote sliding
	windows chosen for further investigation for candidate markers.
}
\label{fig:wrap-slide-window}
\end{figure}

%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\textwidth]{images/wrap-candi.pdf}
\caption[
	61 candidates for primer design for winter-run-associated polymorphisms
]{
	\footnotesize Genomic positions and values of $|d|$ (absolute difference in
	allele frequency between winter run and non-winter run fish of the CCV)
	for the 61 candidate SNPs (in red) to design for winter-run-associated polymorphisms
	(WRAPs).  Other sites are shown in black.  The $x$-axis shows position on
	each chromsome in the Otsh\_v1.0 assembly.  The chromsome name is indicated in the facet headers by
	RefSeq name
}
\label{fig:wrap-slide-window}
\end{figure}

### 2024-07-18 tex/supplemental-text.tex
Big overhaul just before I gave lab meeting about this
A boatload of editing on the paper
Getting WRAP stuff added in to repo and paper/supp

\section{Supplemental Text}

>>>>

\section{Winter-run-associated polymorphism (WRAP) methods and results\label{sec:wrap-methods}}

We used the whole genome sequencing data from \citet{thompson2020complex} to seek variants with
large allele frequency differences between winter-run Chinook salmon and all the other
Chinook salmon ecotypes in the Central Valley of California (CCV).  Because winter-run Chinook are
already highly differentiated from all others, we did not pursue an association study as used
for identifying the late-fall-run associated variants.  Rather, we first identified regions with a high
density of variants with large allele frequency differences between winter-run and non-winter-run
fish in the CCV\@. Subsequently we identified SNPs within those regions with particularly
large allele frequency differences.  This approach was taken to avoid targeting single SNPs
with large allele frequency differences resulting from sampling variation, which was a
concern because we had whole genome sequencing data from only 16 winter run fish.

More specifically, we calculated allele frequencies for 16 winter-run fish and 84 non-winter-run
fish from the  \citet{thompson2020complex} variant data VCF files using ANGSD version~0.921.
Sites were retained if at least 62.5\% of samples in each group had read data (10 of 16 for the
winter run and 50 of 80 for the non-winter run), resulting in 7,295,001 SNPs for downstream
analysis.  We first investigated the distribution throughout the genome of $|d|$, the absolute difference
of the alternate allele frequency between the two groups  (Fig.~\ref{fig:wrap-absdiff}). This revealed
that many loci had large values of $|d|$, but there were several
regions in the genome, in particular, with prominent peaks in allele frequency difference and one
or more SNPs apparently fixed for alternate alleles between the two sample groups.

To leverage information from multiple SNPs to identify regions in the genome with large
allele frequency differences, we calculated the fraction of SNPs with $|d| > 0.5$ that also
had $|d| > 0.9$ within non-overlapping 100 kb sliding windows throughout the genome. This metric indicated
several prominent peaks.  We focused on all of those
100 kb windows in which more than 12.4\% of sites with $|d|>0.5$ also had $|d|>0.9$ which were
also adjacent to at least one window in which $>10\%$ of sites with $|d|>0.5$ also had $|d|>0.9$ 
(Fig.~\ref{fig:wrap-slide-window}).  Within the windows found on four different chromosomes using
the above criteria, we then attempted to design amplicons to type the SNPs at a subset of the sites
within each window.  We chose all sites with $|d|>0.975$, as well as the 8 SNPs on each chromosome
with the highest values of $|d|$.

\comment{ECA has to add the WRAP text here}

THIS TEXT IS JUST IN HERE AS A PLACEHOLDER IN CASE WE WANT TO
HAVE SOME SUPPLEMENTAL TEXT.
